The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-28 manuscript/manuscript.Rnw
fix placenta table and file expansion

All of the code used to produce every analysis presented in this paper
is available at
\url{https://github.com/uiuc-cgm/placenta-viviparous.git}. All of the
sequences used are deposited in SRA, and new sequences for this work
can be obtained under the series
\href{http://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE79121}{GSE79121}
(Supplemental \cref{tab:srr_numbers}). The mean FPKM for gene in each
species with ortholog annotations are located in the supplemental data
files \Sexpr{english.join(paste0(gsub(" ","\\_",
  star.logs[,unique(species)]),"_mean_fpkm.txt"))}.

@@

\begin{table}
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{\linagetableexplanation{primates}}
\label{tab:primate_lineage_specific}
\end{table}

>>>>

All of the code used to produce every analysis presented in this paper
is available at
\url{https://github.com/uiuc-cgm/placenta-viviparous.git}. All of the
sequences used are deposited in SRA, and new sequences for this work
can be obtained under the series
\href{http://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE79121}{GSE79121}
(Supplemental \cref{tab:srr_numbers}). The mean FPKM for gene in each
species with ortholog annotations are located in the supplemental data
files \Sexpr{english.join(gsub("_","\\\\_",paste0(gsub(" ","_",
  star.logs[,unique(species)]),"_mean_fpkm.txt")))}.

@@

\begin{table}
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{primates}{all other analyzed species}}
\label{tab:primate_lineage_specific}
\end{table}
